---
title: "How to Use IsoMemo for Researchers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Use IsoMemo for Reseachers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
- `getRemoteDataAPI()` retrieves the API to query the data
- `getMappingAPI()` calls the mapping for the fields needed from the user API calls
- `getDatabaseList()` returns a list of database names linked to the API call
- `callAPI()` initiates the request to call 
```{r setup}
library(IsoMemo)
getDatabaseList() # returns a character format of list of database names linked to the API call
```

```{r explore data}
df = getData(db="IntChron",category = "Location")
# see latitude and longitude of each site
head(df)
```
The function below retrieves ALL data and fields from all existing databases.
```{r all data}
# ALL_DATA = getData()
# print(nrow(ALL_DATA)) # check how many rows
# levels(ALL_DATA$source) # check all the database sources are there
```


### Let's explore another database: LiVES
```{r descriptives}
getDatabaseList() # tells what database are currently published

df1 = getData('LiVES')
summary(df1)
```


How is the distribution of the variable "d15N" isotope?
```{r hist}
hist(df1$d15N)
```


Let's see the linear relationship between variables d13C and d15N:
```{r regression}
df1 <- na.omit(df1)
lm(d13C~d15N,data=df1)

```
